\bf Fast, Scalable Phrase-Based SMT Decoding

### 2016-09-10 amta.2016/amta2016.tex
ack

% \section*{Acknowledgments}
% 
% Do not number the acknowledgment section.
% This section should not be presented for the submission version.

\small

>>>>

 \section*{Acknowledgments}
This work is sponsored by the Air Force Research Laboratory, prime contract FA8650-11-C-6160.  The views and conclusions contained in this document are those of the authors and should not be interpreted as representative of the official policies, either expressed or implied, of the Air Force Research Laboratory or the U.S. Government.
\small
